---
title: Demonstration of reproducible research using Docker, knitr and rmarkdown
author: |-
    Shripad Sinari\
    Statistics Consulting Laboratory\
    BIO5, The University of Arizona \
    shripad@statlab.bio5.org\
date: '`r Sys.Date()`'
header-includes:
   - \usepackage{pdflscape, booktabs, float, amsmath, amsthm, tcolorbox, array, blkarray, dcolumn}
output:
    pdf_document:
      fig_caption: yes
      keep_tex: true
      includes:
        in_header: header.tex
urlcolor: blue
---

# Introduction

This document is used in a demonstration of reproducible research and some
functionality from the _smisc_ package.

If the docker environment setup has gone correctly and you regenerate this
report in that environment then your should get a PDF file with the same content
as the one in results folder named "demo-original-output.pdf". The only
difference will be the date.

We will use the _iris_ dataset in this example. The smisc package has isolated
functions from _Hmisc_ that provides a descriptive summary of each column in a
dataset. A biplot using ggplot2 package is also implemented. For more
information on smisc, see the [github repo](https://github.com/ssinari/smisc).

# Analysis

We will explain each code chunk here:

1. Load the libraries required for the analysis

```{r ll, echo = TRUE, eval = TRUE, message=FALSE, warning=FALSE, results = "hide"}
library(tidyverse)
library(smisc)
```

2. Load the data set stored in a local file.

```{r load_data, echo = TRUE, eval = TRUE, message=FALSE, warning=FALSE, results = "hide"}
iris_local <- read.csv("../data/iris_local.csv")
```

\clearpage

3. Produce the summary of the data.

```{r iris_summary, echo = TRUE, eval = TRUE, message=FALSE, warning=FALSE, results = "asis"}
summarize(iris_local, "iris")
```

4. Analyse which variables provide the most distinguishing features of the
   different species of iris.

```{r pca, echo = TRUE, eval = TRUE, message=FALSE, warning=FALSE, results = "hide"}
pca <- iris_local %>%
    dplyr::select(-c(ID,Species)) %>%
    as.matrix() %>%
    prcomp()

biplot <- PCbiplot(PC = pca
       , d = iris_local
       , colors = c("#fc8d59","#ffffbf","#91bfdb")
       , legend_t = "Species"
       , varnames = colnames(iris_local)[-grep("ID|Species", colnames(iris_local))]
       , labels = F
       , title = "")
```

\blandscape

```{r biplot, echo = FALSE, eval = TRUE, message=FALSE, warning=FALSE, fig.pos = "H", fig.path='fig/plot-', dev='pdf', fig.ext='pdf', fig.width= 12, fig.height=8, fig.cap = "Biplot of the iris data. Petals (length or width) is the distinguishing feature of an iris species rather than its sepal."}
biplot
```

\elandscape
